Local metal-insulator transition in a generalised impurity Anderson model

### 2022-05-03 gen-siam-manuscript/gen-siam.tex
completed work sections and appendix

\title{Local metal-insulator transition in a generalised impurity Anderson model}
\author{Abhirup Mukherjee}
\email{am18ip014@iiserkol.ac.in }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{Siddhartha Lal}
\email{slal@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}

@@

In order to enhance the Anderson impurity model (AIM), we introduce two extra two-particle interaction terms into the Hamiltonian:
\begin{itemize}
	\item a spin-exchange term \(J \vec{S}_d\cdot\vec{s}_0\) between the impurity spin \(\vec S_d\) and the spin \(\vec s_0\) of the zeroth site 
	\item a local particle-hole symmetric correlation term \(-U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}\) on the zeroth site
\end{itemize}

With these additional terms, the {\it generalised Anderson impurity model} (henceforth referred to as the GAIM), at particle-hole symmetry, is
\begin{equation}\begin{aligned}
	\label{GIAM-ham}
	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \vec{S}_d\cdot\vec{s}_0 \\
	+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
\end{aligned}\end{equation}
All the terms in the Hamiltonian have been depicted schematically in Fig.~\ref{zeromode-bare}.

@@

\subsection{Presence of sub-dominant pair fluctuations}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.49\textwidth]{../figures/odlro.pdf}
	\caption{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator. This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\), which decrease towards the transition.}
	\label{pair_fluc}
\end{figure}

@@

The RG fixed point Hamiltonian describes the low-energy phase of the system. In general, if the RG fixed point is reached at an energy scale \(D^*\), the fixed point Hamiltonian \(\mathcal{H}^*\) is obtained simply from the fixed point values of the couplings, and by noting that the states above \(D^*\) are now part of the IOMs:
\begin{equation}\begin{aligned}
	\mathcal{H}^* = -\frac{1}{2}U^*\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} \\
	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + J^* \vec{S}_d\cdot\vec{s}_0
\end{aligned}\end{equation}

\subsection{Screened regime}
\(U\) is irrelevant in this regime. Moreover, as we go towards the thermodynamic limit by increasing the bandwidth \(D_0\), we find that \(J^* \gg V^*\) (see Fig.~\ref{J_bandwidth}), and the fixed point Hamiltonian is determined purely by the spin-exchange part; combining this with the local bath correlation \(U_b\) that is marginal then gives the low-energy Hamiltonian for the screened regime:
\begin{equation}
	H_\text{eff}^\text{sc} = J^* \vec{S}_d\cdot\vec{s}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow} + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma}
\end{equation}

@@

Since the high momentum modes have been decoupled, the ground state in this regime can be estimated by compressing the kinetic energy to the zero bandwidth limit: 
\begin{equation}\begin{aligned}
	\sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} \sim \epsilon_F \sum_{\vec k_F,\sigma}\tau_{\vec k_F,\sigma}
\end{aligned}\end{equation}
Choosing the chemical potential such that \(\epsilon_F\) vanishes results in a {\it two-site Hamiltonian} composed of the impurity site and the zeroth site (see Fig.~\ref{zero-bw}):
\begin{equation}
	\label{two-site}
	H_\text{eff}^\text{sc} \sim J^* \vec{S}_d\cdot\vec{s}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
\end{equation}
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.4\textwidth]{../figures/zeromode_eff.pdf}
	\caption{Two site Hamiltonian obtained by taking the zero bandwidth limit of the effective Hamiltonian in the screened regime.}
	\label{zero-bw}
\end{figure}
This model is easily solved and the ground state is a maximally-entangled spin singlet formed by \(\vec S_d\) and \(\vec s_0\); the ground state energy is \(E_\text{gs}^\text{sc} = -\frac{3}{4}J^* - U_b\):
\begin{equation}\begin{aligned}
	\ket{\Psi}_\text{gs}^\text{sc} = \frac{1}{\sqrt 2}\left(\ket{\uparrow_d,\downarrow_0} - \ket{\downarrow_d,\uparrow_0}\right)
\end{aligned}\end{equation}
where \(\left\{\uparrow_d, \downarrow_d\right\}, \left\{\uparrow_0, \downarrow_0\right\}\) are the spin states of the impurity and zeroth sites respectively. As mentioned before, this regime in the GAIM is adiabatically connected to the AIM, and indeed, such a spin-singlet ground state is also obtained in the AIM from other methods like Poor Man's scaling~\cite{anderson1969exact,anderson1970}, numerical renormalisation group~\cite{wilson1975,hrk_wilson_1980}, Bethe ansatz~\cite{}, conformal field theory methods~\cite{}[CITE] and the URG analysis of the Kondo model~\cite{anirban_kondo}.

@@

Along the critical points, \(J\) is marginal and \(U\) is irrelevant, while \(V\) is slightly relevant (see Fig.~\ref{rg-flow}). This leads to enhanced fluctuations in both the spin and charge sectors of the impurity site. The effective Hamiltonian is
\begin{equation}\begin{aligned}
	H_\text{eff}^\text{crit} = \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} + J^* \vec{S}_d\cdot\vec{s}_0\\
	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
\end{aligned}\end{equation}
Since the interactions are marginal or only slightly relevant, the kinetic energy is no longer negligible compared to them, and it is not possible to faithfully take a zero bandwidth limit of the problem. 
\subsection{Nature of ground state near the critical point}

@@

\section{Conclusions}

@@

@@

\subsection{Renormalisation of the impurity energy \(\epsilon_d\)}
The coupling \(\epsilon_d\) is renormalised by three kinds of vertices: \(V^2\), \(J^2\) and \(K^2\). We will consider these processes one after another. We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step. In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes. The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom. We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations. The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\). To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\). This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state. Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).

@@

Combining all this, we can write \(E_1 = \frac{D}{2} - \frac{K}{4}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\). In order to relate \(\omega_0\) with \(\omega_1\) with the common fluctuation scale \(\omega\) for the conduction electrons, we will replace these quantum fluctuation scales by the current renormalised values of the single-particle self-energy for the initial state from which we started scattering. For \(\hat n_{d\overline\beta}=0\), there is no additional self-energy because the impurity does not have any spin: \(\omega_0 = \omega\). For \(\hat n_{d\overline\beta} = 1\), we have an additional self-energy of \(\epsilon_d\) arising from the correlation on the impurity: \(\omega_1 = \omega + \epsilon_d\).

@@

	V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)

@@

	V^2 n_j\sum_{\beta}\hat n_{d\beta}\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)

@@

The final kind of scattering is the \(K^2\) type. Similar to the \(J^2\) term, we get the following contribution:
	\label{ren_ed_Kpp}
	\frac{K^2}{4}\sum_{q\beta}c^\dagger_{q\beta}c^\dagger_{q\overline\beta}c_{d\overline\beta}c_{d\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{q\overline\beta}c_{q\beta} = \frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \left(1 - \hat n_{d \uparrow}\right) \left( 1 - \hat n_{d \downarrow} \right)
in the particle sector. This is again because \(E = \frac{D}{2} - \frac{K}{4}\) in the intermediate state and \(\omega^\prime = \omega\). In the hole sector, we get
	\label{ren_ed_Kph}
	\frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \hat n_{d\uparrow}\hat n_{d \downarrow}~.

>>>>

\title{Local metal-insulator transition in a generalised impurity Anderson model}
\author{Abhirup Mukherjee}
\email{am18ip014@iiserkol.ac.in }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{N. S. Vidhyadhiraja}
\email{raja@jncasr.ac.in}
\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
\author{A. Taraphder}
\email{arghya@phy.iitkgp.ernet.in}
\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
\author{Siddhartha Lal}
\email{slal@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}

@@

In order to enhance the Anderson impurity model (AIM), we introduce two extra two-particle interaction terms into the Hamiltonian:
\begin{itemize}
	\item a spin-exchange term \(J \vec{S}_d\cdot\vec{S}_0\) between the impurity spin \(\vec S_d\) and the spin \(\vec S_0\) of the zeroth site 
	\item a local particle-hole symmetric correlation term \(-U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}\) on the zeroth site
\end{itemize}

With these additional terms, the {\it generalised Anderson impurity model} (henceforth referred to as the GAIM), at particle-hole symmetry, is
\begin{equation}\begin{aligned}
	\label{GIAM-ham}
	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \vec{S}_d\cdot\vec{S}_0 \\
	+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
\end{aligned}\end{equation}
All the terms in the Hamiltonian have been depicted schematically in Fig.~\ref{zeromode-bare}.

@@

\subsection{Growth of charge isospin fluctuations in the bath}
The low-energy phase of the AIM is characterised by enhanced spin-fluctuation \(\left<S_d^+S_0^- + \text{h.c.}\right>\); these fluctuations arise from the Kondo cloud and they serve to screen the local moment. For the system to undergo a transition into an unscreened regime, these fluctuations must get replaced by those of a different kind. This is shown in Fig.~\ref{pair_fluc}, where we plot not only the spin fluctuations mentioned, but also two-particle charge fluctuations \(\left<c^\dagger_{\vec k \uparrow} c^\dagger_{\vec k \downarrow} c_{\vec k^\prime \uparrow} c_{\vec k^\prime \downarrow}\right>\) in the bath that transfer holons and doublons across \(k-\)states. We find that while the former decrease towards the transition, the latter pick up; the spin-fluctuations are getting replaced by the charge fluctuations. This is substantied by the inset of the same figure, which shows the behaviour of these fluctuations even after the transition. While the spin-fluctuations vanish beyond the transition, the charge fluctuations undergo an abrupt increase.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.49\textwidth]{../figures/odlro.pdf}
	\caption{Growth in the pair-fluctuation terms \(c^\dagger_{k \uparrow}c^\dagger_{k \downarrow} c_{k^\prime \downarrow}c_{k^\prime \uparrow}\), as \(r \to 0.25\). This comes at the cost of the spin-flip fluctuations \(S_d^+ S_0^- + \text{h.c.}\), which decrease towards the transition. The inset plots the same quantities but for a larger range of \(r\), and the pair fluctuations are seen to pick up abruplty after the transition while the spin fluctuations vanish.}
	\label{pair_fluc}
\end{figure}

@@

The RG fixed point Hamiltonian describes the low-energy phase of the system. In general, if the RG fixed point is reached at an energy scale \(D^*\), the fixed point Hamiltonian \(\mathcal{H}^*\) is obtained simply from the fixed point values of the couplings, and by noting that the states above \(D^*\) are now part of the IOMs:
\begin{equation}\begin{aligned}
	\mathcal{H}^* = -\frac{1}{2}U^*\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} \\
	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + J^* \vec{S}_d\cdot\vec{S}_0
\end{aligned}\end{equation}

\subsection{Screened regime}
\(U\) is irrelevant in this regime. Moreover, as we go towards the thermodynamic limit by increasing the bandwidth \(D_0\), we find that \(J^* \gg V^*\) (see Fig.~\ref{J_bandwidth}), and the fixed point Hamiltonian is determined purely by the spin-exchange part; combining this with the local bath correlation \(U_b\) that is marginal then gives the low-energy Hamiltonian for the screened regime:
\begin{equation}
	H_\text{eff}^\text{sc} = J^* \vec{S}_d\cdot\vec{S}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow} + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma}
\end{equation}

@@

Since the high momentum modes have been decoupled, the ground state in this regime can be estimated by compressing the kinetic energy to the zero bandwidth limit: 
\begin{equation}\begin{aligned}
	\sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} \sim \epsilon_F \sum_{\vec k_F,\sigma}\tau_{\vec k_F,\sigma}
\end{aligned}\end{equation}
Choosing the chemical potential such that \(\epsilon_F\) vanishes results in a {\it two-site Hamiltonian} composed of the impurity site and the zeroth site (see Fig.~\ref{zero-bw}):
\begin{equation}
	\label{two-site}
	H_\text{eff}^\text{sc} \sim J^* \vec{S}_d\cdot\vec{S}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
\end{equation}
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.4\textwidth]{../figures/zeromode_eff.pdf}
	\caption{Two site Hamiltonian obtained by taking the zero bandwidth limit of the effective Hamiltonian in the screened regime.}
	\label{zero-bw}
\end{figure}
This model is easily solved and the ground state is a maximally-entangled spin singlet formed by \(\vec S_d\) and \(\vec S_0\); the ground state energy is \(E_\text{gs}^\text{sc} = -\frac{3}{4}J^* - U_b\):
\begin{equation}\begin{aligned}
	\ket{\Psi}_\text{gs}^\text{sc} = \frac{1}{\sqrt 2}\left(\ket{\uparrow_d,\downarrow_0} - \ket{\downarrow_d,\uparrow_0}\right)
\end{aligned}\end{equation}
where \(\left\{\uparrow_d, \downarrow_d\right\}, \left\{\uparrow_0, \downarrow_0\right\}\) are the spin states of the impurity and zeroth sites respectively. As mentioned before, this regime in the GAIM is adiabatically connected to the AIM, and indeed, such a spin-singlet ground state is also obtained in the AIM from other methods like Poor Man's scaling~\cite{anderson1969exact,anderson1970}, numerical renormalisation group~\cite{wilson1975,hrk_wilson_1980}, Bethe ansatz~\cite{}, conformal field theory methods~\cite{}[CITE] and the URG analysis of the Kondo model~\cite{anirban_kondo}.

@@

Along the critical points, \(J\) is marginal and \(U\) is irrelevant, while \(V\) is slightly relevant (see Fig.~\ref{rg-flow}). This leads to enhanced fluctuations in both the spin and charge sectors of the impurity site. The effective Hamiltonian is
\begin{equation}\begin{aligned}
	H_\text{eff}^\text{crit} = \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} + J^* \vec{S}_d\cdot\vec{S}_0\\
	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
\end{aligned}\end{equation}
Since the interactions are marginal or only slightly relevant, the kinetic energy is no longer negligible compared to them, and it is not possible to faithfully take a zero bandwidth limit of the problem. 
\subsection{Nature of ground state near the critical point}

@@

\section{Discussions and Outlook}

@@

\bibliography{gen-siam}

@@

\subsection{Some preliminaries}
The Hamiltonian we are working with is the generalised Anderson impurity model (Eq.~\ref{GIAM-ham}):
\begin{equation}\begin{aligned}
	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \sum_{\vec k,\vec k^\prime,\atop{\alpha,\beta}}\vec{S}_d\cdot\vec{\sigma}_{\alpha\beta}c^\dagger_{\vec k,\alpha}c_{\vec k^\prime,\beta} + V\sum_{\vec k,\sigma} \left( c^\dagger_{d\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) - U_b \sum_{\vec k,\vec k^\prime,\sigma}c^\dagger_{\vec k,\sigma}c_{\vec k^\prime,\sigma} \\
+ U_b \sum_{\vec k_1,\vec k_2,\atop{\vec k_3,\vec k_4}}c^\dagger_{\vec k_1 \uparrow} c_{\vec k_2 \uparrow} c^\dagger_{\vec k_3 \downarrow} c_{\vec k_4 \downarrow}
\end{aligned}\end{equation}
The renormalisation in the Hamiltonian \(H_{(j)}\) at the \(j^\text{th}\) RG step, upon decoupling an electronic state \(q\beta\), is given by the expression:
\begin{equation}\begin{aligned}
	\left(\Delta H_{(j)}\right)_{\vec q,\beta} = H_{(j-1)} - H_{(j)} = c^\dagger_{\vec q,\beta} T_{\vec q,\beta} \frac{1}{\omega_e - H_D} T^\dagger_{\vec q,\beta}c_{\vec q,\beta} + T^\dagger_{\vec q,\beta} c_{\vec q,\beta} \frac{1}{\omega_h - H_D} c^\dagger_{\vec q,\beta}T_{\vec q,\beta}~,
\end{aligned}\end{equation}
where \(\omega_{e,h}\) are the quantum fluctuation scales for the electron and hole scattering channels, \(H_D\) is the part of the Hamiltonian that is diagonal in \(k-\)space, and \(T_{\vec q,\beta} + T_{\vec q,\beta}^\dagger\) is the part of the Hamiltonian that does not commute with \(\hat n_{\vec q,\beta}\) (in short, it is the part that is off-diagonal with respect to a particular state \(\vec q,\beta\)). This off-diagonal part is made up of contributions from \(V,J\) and \(U_b\):
\begin{equation}\begin{aligned}
	T_{\vec q \uparrow} = \left[V c^\dagger_{d \uparrow}  + J \sum_{\vec k}S_d^+ c^\dagger_{\vec k \downarrow}  + U_b \sum_{\vec k_1,\vec k_2,\vec k_3}c^\dagger_{\vec k_1 \uparrow} c^\dagger_{\vec k_3 \downarrow} c_{\vec k_4 \downarrow}\right] c_{\vec q \uparrow} ~,
\end{aligned}\end{equation}
while the diagonal part is given by
\begin{equation}\begin{aligned}
	H_D = \epsilon_{\vec q} \tau_{q\uparrow} + \frac{1}{4}J S_d^z\left(\hat n_{q \uparrow} - \hat n_{q \downarrow}\right) - U_b \left(\tau_{\vec q,\uparrow}\right)^2~,
\end{aligned}\end{equation}
where we have rewritten \(\hat n_{\vec q,\beta}\) in terms of \(\tau_{\vec q,\beta} \equiv \hat n_{\vec q,\beta} - \frac{1}{2}\) in the contribution from \(U_b\). Note that we have ignored a potential scattering term in the off-diagonal part \(T_{\vec q\beta}\). In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0. For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\). Because the diagonal contribution from \(U_b\) always changes the energy of the excited energy by \(-U_b/4\),  the denominator will simply change by \(U_b/4\) (\(H_D\) comes with a minus sign in the denominator). We will suppress this change for now and substitute in all the denominators at the end.

We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step. In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes. The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom. We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations. The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\). To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\). This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state. Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).

\subsection{Renormalisation of \(U_b\)}
\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
\begin{equation}\begin{aligned}
	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
\end{aligned}\end{equation}
In order to renormalise \(U_b\), we need to contract one more pair of momenta. There are two choices. The first is by setting \(k_3 = k_3^\prime = q\). The two internal states, then, are \(q\beta\) and \(q\overline\beta\). As discussed above, the intermediate state energy is \(-U_b/4\). We therefore have
\begin{equation}\begin{aligned}
	\frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
\end{aligned}\end{equation}
Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
\begin{equation}\begin{aligned}
	\frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
\end{aligned}\end{equation}
The two contributions cancel each other. The same cancellation happens in the hole sector as well.

\subsection{Renormalisation of the impurity correlation \(U\)}
The coupling \(U\) is renormalised by two kinds of vertices: \(V^2\) and \(J^2\). We will consider these processes one at a time. For convenience, we define \(\epsilon_d = -U/2\).

@@

Combining all this, we can write \(E_1 = \frac{D}{2}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\). In order to relate \(\omega_0\) with \(\omega_1\) with the common fluctuation scale \(\omega\) for the conduction electrons, we will replace these quantum fluctuation scales by the current renormalised values of the single-particle self-energy for the initial state from which we started scattering. For \(\hat n_{d\overline\beta}=0\), there is no additional self-energy because the impurity does not have any spin: \(\omega_0 = \omega\). For \(\hat n_{d\overline\beta} = 1\), we have an additional self-energy of \(\epsilon_d\) arising from the correlation on the impurity: \(\omega_1 = \omega + \epsilon_d\).

@@

	V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} + \epsilon_d}\right)

@@

	V^2 n_j\sum_{\beta}\hat n_{d\beta}\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} + \epsilon_d} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)

@@

We now have all possible renormalisation to the impurity correlation \(U\). To actually compute the renormalisation, we will first calculate the renormalisation in the energies \(\epsilon_0, \epsilon_1\) and \(\epsilon_2\) of the impurity states \(\ket{\hat n_d = 0}, \ket{\hat n_d = 1}, \ket{\hat n_d = 2}\) respectively. The renormalisation of these states are given by the following terms:
\begin{itemize}
	\item \(\Delta \epsilon_0\) is given by the renormalisation of the term \(\left(1 - \hat n_{d\uparrow}\right)\left(1 - \hat n_{d \downarrow}\right)\)
	\item \(\Delta \epsilon_1\) is given by the renormalisation of either \(\left(1 - \hat n_{d\uparrow}\right)\hat n_{d \downarrow}\) or \(\left(1 - \hat n_{d\downarrow}\right)\hat n_{d \uparrow}\)
	\item \(\Delta \epsilon_2\) is given by the renormalisation of \(\hat n_{d\uparrow}\hat n_{d \downarrow}\)
\end{itemize}
From eqs.~\ref{ren_ed_Vp}, \ref{ren_ed_Vh}, \ref{ren_ed_Jpp} and \ref{ren_ed_Jph}, we write
\begin{equation}\begin{aligned}
	\Delta U = \Delta \epsilon_2 + \Delta \epsilon_0 - 2\Delta \epsilon_1 = -\frac{4V^2 n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} - U/2} + \frac{4V^2 n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} + U/2 + \frac{J}{4}} - \frac{J^2n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,
\end{aligned}\end{equation}
where we have restored the contribution from \(U_b\) in the denominator.

\subsection{Renormalisation of the hybridisation \(V\)}
Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VU_b\). Within the first kind, the scattering can be either via \(S_d^z\) or through \(S_d^\pm\). For the first kind, we have the following contribution in the particle sector:
\begin{equation}\begin{aligned}
	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} = \frac{1}{4}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\sum_{k\beta} \left(1 - \hat n_{d\overline\beta}\right) c_{d\beta}c^\dagger_{k\beta}
\end{aligned}\end{equation}
The transformation from \(\frac{1}{\omega - H_D}\) to \(\frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\) is made so that we can account for both the initial state and the final state energies through the two fluctuation scales \(\omega^\prime_1\) and \(\omega_2^\prime\) respectively; we calculate the denominators for both the initial and final states, and then take the mean of the two (hence the factor of half in front). This was not required previously because in the earlier scattering processes, the impurity returned to its initial state at the end, at least in terms of \(\epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 \), and so we had \(\omega_1^\prime = \omega_2^\prime = \omega^\prime\).
